---
title: "AssignmentV"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Setting up a new GitHub repository

The project on GitHub is named "DSPM_AssignmentV", it can be accessed with the following link:
https://github.com/kevin19982/DSPM_AssignmentV


## 2. Getting to know the API

The API-key is stored in a separate file, which is ignored when pushing changes to the repository.
It is stored in a file named "api_key.R"


## 3. Interacting with the API - the basics

First the environment is cleared and the set up conducted.
```{r set up, warning = FALSE, message = FALSE}

# clear workspace
rm(list = ls())

# load relevant libraries
library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)
library(dplyr)

# load the key
source("api_key.R")

```

According to the description on the website of ticketmaster the get-command is written, that extracts information about events in germany.
```{r get query}

# get event venues in germany
event_ger <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=DE&",
                 query = list(apikey = api_key)) %>% content()

```
The resulting object contains a list with the name "_embedded", which includes the extracted events, which in this case is 20, and information about them. There is also a list "_links", which includes information about the query and a list named "page", that includes information about the data (pagesize, number of pages etc.).

Extracting the relevant information and adding it to a dataframe. The size of the dataframe is predefined for faster computation.
```{r extract information}

# command to get the required elements
event <- event_ger[["_embedded"]]$events[[1]][["_embedded"]]$venues[[1]]$city$name

# number of observations
n <- 20

event_info <- tibble(
  name <- character(n),
  city <- character(n),
  postalCode <- character(n),
  address <- character(n),
  url <- character(n),
  longitude <- character(n),
  latitude <- character(n)
)

for (i in 1:20){
  event_info[i, 1] <- event_ger[["_embedded"]]$venues[[i]]$name
  event_info[i, 2] <- event_ger[["_embedded"]]$venues[[i]]$city$name
  event_info[i, 3] <- event_ger[["_embedded"]]$venues[[i]]$postalCode
  event_info[i, 4] <- event_ger[["_embedded"]]$venues[[i]]$address
  event_info[i, 5] <- event_ger[["_embedded"]]$venues[[i]]$url
  if (is.null(event_ger[["_embedded"]]$venues[[i]]$location$longitude)) {
    event_info[i, 6] <- NA
    event_info[i, 7] <- NA
  } else {
  event_info[i, 6] <- event_ger[["_embedded"]]$venues[[i]]$location$longitude
  event_info[i, 7] <- event_ger[["_embedded"]]$venues[[i]]$location$latitude
  }
}

# check the extracted data
glimpse(event_info)

```


## 4. Interacting with the API - advanced

All the venues in germany can be extracted by using the venue search and adding "DE" as a country code. Assigning of values does not work if the field has no entry in the data, hence in this case NA's are assigned.
```{r complete data}

# check what using venue search retrieves
event_info_complete <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                           query = list(apikey = api_key,
                           countryCode = "DE")) %>% content()

# number of results
n <- as.numeric(event_info_complete[["page"]]$totalElements)
print(n)

# number of elements per complete page
page_size <- as.numeric(event_info_complete[["page"]]$size)

# number of complete pages
pages_complete <- floor(n/page_size)

# number of entries on the last page
rest_complete <- n - page_size * floor(n/page_size) # number of total elements - accumulated number of elements on complete pages

# create result data frame
event_info_complete <- tibble(
  name <- character(n),
  city <- character(n),
  postalCode <- character(n),
  address <- character(n),
  url <- character(n),
  longitude <- character(n),
  latitude <- character(n))

# retrieve complete data
for (i in 1:pages_complete - 1) { # appearently the pages start at 0
  result_event <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                      query = list(apikey = api_key,
                                   countryCode = "DE",
                                   page = i)) 
  
  event_content <- content(result_event)
  
  # delay the next operation to retrieve information less than 5 times per second
  Sys.sleep(0.2)
  
  # retrieve the specific information, it does not work for some observation, because they do not include every variable, hence there are NA-values assigned
  for (t in 1:page_size) {
    if (is.null(event_content[["_embedded"]]$venues[[t]]$name)) {
      event_info_complete[(i) * page_size + t, 1] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 1] <- event_content[["_embedded"]]$venues[[t]]$name
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$city$name)) {
      event_info_complete[(i) * page_size + t, 2] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 2] <- event_content[["_embedded"]]$venues[[t]]$city$name
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$postalCode)) {
      event_info_complete[(i) * page_size + t, 3] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 3] <- event_content[["_embedded"]]$venues[[t]]$postalCode
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$address$line1)) {
      event_info_complete[(i) * page_size + t, 4] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 4] <- event_content[["_embedded"]]$venues[[t]]$address$line1
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$url)) {
      event_info_complete[(i) * page_size + t, 5] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 5] <- event_content[["_embedded"]]$venues[[t]]$url
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$location$longitude)) {
      event_info_complete[(i) * page_size + t, 6] <- NA
      event_info_complete[(i) * page_size + t, 7] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 6] <- event_content[["_embedded"]]$venues[[t]]$location$longitude
      event_info_complete[(i) * page_size + t, 7] <- event_content[["_embedded"]]$venues[[t]]$location$latitude
    }
  }
  
}


# adding values from the last page, counting i up by 1 to do so
i = i + 1

# getting the values from the last page
result_event <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                      query = list(apikey = api_key,
                                   countryCode = "DE",
                                   page = i))

# adding the values from the last page to the dataframe
for (t in 1:page_size) {
    if (is.null(event_content[["_embedded"]]$venues[[t]]$name)) {
      event_info_complete[(i) * page_size + t, 1] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 1] <- event_content[["_embedded"]]$venues[[t]]$name
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$city$name)) {
      event_info_complete[(i) * page_size + t, 2] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 2] <- event_content[["_embedded"]]$venues[[t]]$city$name
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$postalCode)) {
      event_info_complete[(i) * page_size + t, 3] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 3] <- event_content[["_embedded"]]$venues[[t]]$postalCode
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$address$line1)) {
      event_info_complete[(i) * page_size + t, 4] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 4] <- event_content[["_embedded"]]$venues[[t]]$address$line1
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$url)) {
      event_info_complete[(i) * page_size + t, 5] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 5] <- event_content[["_embedded"]]$venues[[t]]$url
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$location$longitude)) {
      event_info_complete[(i) * page_size + t, 6] <- NA
      event_info_complete[(i) * page_size + t, 7] <- NA
    } else {
      event_info_complete[(i) * page_size + t, 6] <- event_content[["_embedded"]]$venues[[t]]$location$longitude
      event_info_complete[(i) * page_size + t, 7] <- event_content[["_embedded"]]$venues[[t]]$location$latitude
    }
  }


colnames(event_info_complete) <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")

# check the extracted data
glimpse(event_info_complete)

```


## 5. Visualizing the extracted data

Drawing the map of germany and adding the points of the location, so their location is visible on the map.
```{r map of germany}

# excluding extreme values
event_info_complete_graphversion <- event_info_complete %>% filter(between(longitude, 5.866944, 15.043611))
event_info_complete_graphversion <- event_info_complete_graphversion %>% filter(between(latitude, 47.271679, 55.0846))

# drawing the plot, longitude and latitude are characters, hence there are transformed to numeric values
ggplot() + 
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
    fill = "grey90", color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size = 8, face = 'bold'),
        plot.caption = element_text(face = "italic")) +  geom_point(aes(x = as.numeric(longitude), y = as.numeric(latitude)), data = event_info_complete_graphversion, col = "red", size = 1)

```
Some points are outside the map of germany, since the filter commands defined a rectangle (with a dimension of approximately 7x8).


## 6. Event locations in other countries

Repeating the operations for france.
First, conduct a get request for france in general for the first page.
```{r event locations france}


# get event venues in france
event_fr <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=FR&",
                 query = list(apikey = api_key)) %>% content()


```

Then get the relevant information from the first page (as with germany before). Luckily the structure of the data is the same as for germany.
```{r information france}

# command to get the required elements
event <- event_fr[["_embedded"]]$events[[1]][["_embedded"]]$venues[[1]]$city$name

# number of observations
n_fr <- 20

event_info_fr <- tibble(
  name <- character(n_fr),
  city <- character(n_fr),
  postalCode <- character(n_fr),
  address <- character(n_fr),
  url <- character(n_fr),
  longitude <- character(n_fr),
  latitude <- character(n_fr)
)

for (i in 1:20){
  event_info_fr[i, 1] <- event_fr[["_embedded"]]$venues[[i]]$name
  event_info_fr[i, 2] <- event_fr[["_embedded"]]$venues[[i]]$city$name
  event_info_fr[i, 3] <- event_fr[["_embedded"]]$venues[[i]]$postalCode
  if (is.null(event_fr[["_embedded"]]$venues[[i]]$address$line1)) {
    event_info_fr[i, 4] <- NA
  } else {
  address_fr_1 <- event_fr[["_embedded"]]$venues[[i]]$address$line1
  address_fr_2 <- event_fr[["_embedded"]]$venues[[i]]$address$line2
  event_info_fr[i, 4] <- paste(address_fr_1, address_fr_2, sep = " ")
  }
  if (is.null(event_fr[["_embedded"]]$venues[[i]]$url)) {
    event_info_fr[i, 5] <- NA
  } else {
  event_info_fr[i, 5] <- event_fr[["_embedded"]]$venues[[i]]$url
  }
  if (is.null(event_fr[["_embedded"]]$venues[[i]]$location$longitude)) {
    event_info_fr[i, 6] <- NA
    event_info_fr[i, 7] <- NA
  } else {
  event_info_fr[i, 6] <- event_fr[["_embedded"]]$venues[[i]]$location$longitude
  event_info_fr[i, 7] <- event_fr[["_embedded"]]$venues[[i]]$location$latitude
  }
}

# check the extracted data
glimpse(event_info_fr)

```

The next step is to get all the available data of event venues in france.
```{r event venues france all}

# check what using venue search retrieves
event_info_complete_fr <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                           query = list(apikey = api_key,
                           countryCode = "FR")) %>% content()

# number of results
n_fr <- as.numeric(event_info_complete_fr[["page"]]$totalElements)
print(n_fr)

# number of elements per complete page
page_size_fr <- as.numeric(event_info_complete_fr[["page"]]$size)

# number of complete pages
pages_complete_fr <- floor(n_fr/page_size_fr)

# number of entries on the last page
rest_complete_fr <- n_fr - page_size_fr * floor(n_fr/page_size_fr) # number of total elements - accumulated number of elements on complete pages

# create result data frame
event_info_complete_fr <- tibble(
  name <- character(n_fr),
  city <- character(n_fr),
  postalCode <- character(n_fr),
  address <- character(n_fr),
  url <- character(n_fr),
  longitude <- character(n_fr),
  latitude <- character(n_fr))

# retrieve complete data
for (i in 1:pages_complete_fr - 1) { # appearently the pages start at 0
  result_event_fr <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                      query = list(apikey = api_key,
                                   countryCode = "FR",
                                   page = i)) 
  
  event_content_fr <- content(result_event_fr)
  
  # delay the next operation to retrieve information less than 5 times per second
  Sys.sleep(0.2)
  
  # retrieve the specific information, it does not work for some observation, because they do not include every variable, hence there are NA-values assigned
  for (t in 1:page_size_fr) {
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$name)) {
      event_info_complete_fr[(i) * page_size_fr + t, 1] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 1] <- event_content_fr[["_embedded"]]$venues[[t]]$name
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$city$name)) {
      event_info_complete_fr[(i) * page_size_fr + t, 2] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 2] <- event_content_fr[["_embedded"]]$venues[[t]]$city$name
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$postalCode)) {
      event_info_complete_fr[(i) * page_size_fr + t, 3] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 3] <- event_content[["_embedded"]]$venues[[t]]$postalCode
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$address$line1)) {
      event_info_complete_fr[(i) * page_size_fr + t, 4] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 4] <- event_content_fr[["_embedded"]]$venues[[t]]$address$line1
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$url)) {
      event_info_complete_fr[(i) * page_size_fr + t, 5] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 5] <- event_content_fr[["_embedded"]]$venues[[t]]$url
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$location$longitude)) {
      event_info_complete_fr[(i) * page_size_fr + t, 6] <- NA
      event_info_complete_fr[(i) * page_size_fr + t, 7] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 6] <- 
        event_content_fr[["_embedded"]]$venues[[t]]$location$longitude
      event_info_complete_fr[(i) * page_size_fr + t, 7] <- 
        event_content_fr[["_embedded"]]$venues[[t]]$location$latitude
    }
  }
  
}


# adding values from the last page, counting i up by 1 to do so
i = i + 1

# getting the values from the last page
result_event_fr <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                      query = list(apikey = api_key,
                                   countryCode = "FR",
                                   page = i))

# adding the values from the last page to the dataframe
for (t in 1:page_size_fr) {
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$name)) {
      event_info_complete_fr[(i) * page_size_fr + t, 1] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 1] <- event_content_fr[["_embedded"]]$venues[[t]]$name
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$city$name)) {
      event_info_complete_fr[(i) * page_size_fr + t, 2] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 2] <- event_content_fr[["_embedded"]]$venues[[t]]$city$name
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$postalCode)) {
      event_info_complete_fr[(i) * page_size_fr + t, 3] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 3] <- event_content_fr[["_embedded"]]$venues[[t]]$postalCode
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$address$line1)) {
      event_info_complete_fr[(i) * page_size_fr + t, 4] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 4] <- event_content_fr[["_embedded"]]$venues[[t]]$address$line1
    }
    
    if (is.null(event_content_fr[["_embedded"]]$venues[[t]]$url)) {
      event_info_complete_fr[(i) * page_size_fr + t, 5] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 5] <- event_content_fr[["_embedded"]]$venues[[t]]$url
    }
    
    if (is.null(event_content[["_embedded"]]$venues[[t]]$location$longitude)) {
      event_info_complete_fr[(i) * page_size_fr + t, 6] <- NA
      event_info_complete_fr[(i) * page_size_fr + t, 7] <- NA
    } else {
      event_info_complete_fr[(i) * page_size_fr + t, 6] <- event_content[["_embedded"]]$venues[[t]]$location$longitude
      event_info_complete_fr[(i) * page_size_fr + t, 7] <- event_content[["_embedded"]]$venues[[t]]$location$latitude
    }
  }


colnames(event_info_complete_fr) <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")

# check the extracted data
glimpse(event_info_complete_fr)

```
Ticketmaster stored 91 locations in france, hence this calculation was rather fast.

The next step is to draw the map and add the locations.
```{r map of france}

# excluding extreme values
event_info_complete_graphversion_fr <- event_info_complete_fr %>% filter(between(longitude, 4, 8))
event_info_complete_graphversion_fr <- event_info_complete_graphversion_fr %>% filter(between(latitude, 42, 51))

# drawing the plot
ggplot() + 
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "France"),
    fill = "grey90", color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across France", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size = 8, face = 'bold'),
        plot.caption = element_text(face = "italic")) +
  geom_point(aes(x = as.numeric(longitude), y = as.numeric(latitude)), data = event_info_complete_graphversion_fr, col = "red", size = 2)

```

In this case the filter command also indirectly defined a rectangle, but all the relevant points are inside the map.
